---
title: "JTF003-EC Results"
date: "`r Sys.Date()`"
format: 
  docx:
    number-sections: true
    grid:
      margin-width: 350px
  html:
    toc: true 
    number-sections: true
    grid:
      margin-width: 350px
  pdf:
    toc: true 
    documentclass: article
    fontsize: 8pt
    geometry: "left=1in, right=1in, top=1in, bottom=1in, marginparwidth=2in" 
    include-in-header: 
      text: |
        \usepackage{unicode-math}
        \setmainfont{DejaVu Sans}
editor: source
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)

# setup
library(lme4)
library(kableExtra)
library(tidyverse)
library(patchwork)
library(sjPlot)
library(gt)

library(psych)

# plot theme
ml_theme <- function(base_size = 9, base_family = "Helvetica") {
  theme_bw(
    base_size = base_size,
    base_family = base_family
  ) +
    theme(
      text = element_text(
        family = base_family,
        size = base_size
      ),

      panel.border = element_blank(),

      strip.background = element_rect(
        fill = "white",
        colour = NA
      ),
      strip.text = element_text(
        size = rel(0.8)
      ),

      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_blank(),
      panel.grid.minor = element_blank(),

      axis.line = element_line(
        linewidth = 0.4
      ),
      axis.text.x = element_text(
        size = 7,
        colour = "black"
      ),
      axis.text.y = element_text(
        size = 7,
        colour = "black"
      ),
      axis.ticks = element_line(
        colour = "black"
      )
    )
}
```



```{r load_data, include=FALSE}
# dataset

d <- read_csv("all_withNorway_noTest_countryFill_raw.csv")

```


\newpage

# Results

## Data Processing and Exclusions


Exclusion criteria applied as stated in the [preregistration](https://osf.io/preprints/psyarxiv/wegc5_v1):

> We will exclude participants who did not complete the study, failed an attention check question, failed to pass the Captcha test (i.e., their Captcha score is equal to or lower than 0.5), or are not permanent residents of the geopolitical region where data collection is taking place.

```{r, echo=FALSE}
total_initial <- nrow(d)

# Finished == 1
excluded_finished <- total_initial  - nrow(d %>% filter(Finished == 1))
remaining_after_finished <- nrow(d %>% filter(Finished == 1))

# Matteo note: following prereg literally, but could make sense to look instead at Progress >= ** to include some partial responses

# Q_RecaptchaScore > 0.5
excluded_recaptcha <- remaining_after_finished - nrow(d %>% filter(Finished == 1, 
                                                                   Q_RecaptchaScore >= 0.5))
remaining_after_recaptcha <- nrow(d %>% filter(Finished == 1, 
                                               Q_RecaptchaScore >= 0.5))

# attention check
excluded_attcheck <- remaining_after_recaptcha - nrow(d %>% filter(Finished == 1, 
                                                                   Q_RecaptchaScore >= 0.5,
                                                                   check==0))
remaining_after_attcheck <- nrow(d %>% filter(Finished == 1, 
                                               Q_RecaptchaScore >= 0.5,
                                               check==0))

# country of residence
excluded_residence <- remaining_after_attcheck - nrow(d %>% filter(Finished == 1, 
                                                                   Q_RecaptchaScore >= 0.5,
                                                                   check==0,
                                                                   Country_Res_YN =="Yes"))
remaining_after_residence <- nrow(d %>% filter(Finished == 1, 
                                               Q_RecaptchaScore >= 0.5,
                                               check==0,
                                               Country_Res_YN =="Yes"))

# Total number of participants excluded (excluded because they fail at least 1 criterion)
total_excluded <- total_initial - remaining_after_attcheck

# Create summary table
summary_table <- data.frame(
  Criterion = c( "Finished == 1", 
                 "Q_RecaptchaScore >= 0.5", 
                 "attention check == 0",
                 "Country_Res_YN == Yes",
                 "Total"),
  Excluded = c(excluded_finished, 
               excluded_recaptcha, 
               excluded_attcheck,
               excluded_residence,
               total_excluded),
  Fraction = c(excluded_finished/total_initial, 
               excluded_recaptcha/total_initial, 
               excluded_attcheck/total_initial,
               excluded_residence/total_initial, 
               total_excluded/total_initial),
  Percentage = c(excluded_finished/total_initial * 100, 
                 excluded_recaptcha/total_initial * 100, 
                 excluded_attcheck/total_initial * 100,
                 excluded_residence/total_initial * 100, 
                 total_excluded/total_initial * 100)
)

# # Print the summary table as an HTML table
# kable(summary_table, booktabs = TRUE, 
#       col.names = c("Exclusion Criterion", 
#                     "Number Excluded", 
#                     "Fraction Excluded", 
#                     "Percentage Excluded"), 
#       caption="Each line indicates how many participants failed each criterion (applied sequentially).") %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

# Print the summary table 
kable(summary_table, booktabs = TRUE, 
      col.names = c("Exclusion Criterion", 
                    "Number Excluded", 
                    "Fraction Excluded", 
                    "Percentage Excluded"), 
      caption="Each line indicates how many participants failed each criterion (applied sequentially).")
```




```{r apply_exclusions, include=FALSE}
d <- d %>%
  filter(Finished == 1,
         check == 0,
         Q_RecaptchaScore >= 0.5,
         Country_Res_YN =="Yes")
```



```{r data_preparation,  include=FALSE}

# Expand country names
d <- d %>%
  mutate(Country = recode(Country,
                          "AU" = "Australia",
                          "AT" = "Austria",
                          "AL" = "Albania",
                          "BD" = "Bangladesh",
                          "BA" = "Bosnia-Herzegovina",
                          "BE" = "Belgium", 
                          "BR" = "Brazil",
                          "BG" = "Bulgaria",
                          "CM" = "Cameroon",
                          "CA" = "Canada",
                          "CL" = "Chile",
                          "CN" = "China",
                          "CO" = "Colombia",
                          "HR" = "Croatia",
                          "CY" = "Cyprus",
                          "CZ" = "Czech Republic",
                          "DK" = "Denmark",
                          "EC" = "Ecuador",
                          "EG" = "Egypt",
                          "ET" = "Ethiopia",
                          "FR" = "France",
                          "GE" = "Georgia",
                          "DE" = "Germany",
                          "GH" = "Ghana",
                          "GR" = "Greece",
                          "HK,HK" = "Hong Kong",
                          "HK" = "Hong Kong",
                          "HU" = "Hungary",
                          "IN" = "India",
                          "ID" = "Indonesia",
                          "IR" = "Iran",
                          "IQ" = "Iraq",
                          "IL" = "Israel",
                          "IT" = "Italy",
                          "|T" = "Italy",
                          "JP" = "Japan",
                          "KZ" = "Kazakhstan",
                          "KE" = "Kenya",
                          "XK" = "Kosovo",
                          "KW" = "Kuwait",
                          "LV" = "Latvia",
                          "LB" = "Lebanon",
                          "MY" = "Malaysia",
                          "MX" = "Mexico",
                          "MA" = "Morocco",
                          "NA" = "Namibia",
                          "NZ" = "New Zealand",
                          "NG" = "Nigeria",
                          "MK" = "North Macedonia",
                          "NO" = "Norway",
                          "PK" = "Pakistan",
                          "PH" = "Philippines",
                          "PH,PH" = "Philippines",
                          "PL" = "Poland",
                          "PT" = "Portugal",
                          "RO" = "Romania",
                          "RU" = "Russia",
                          "SA" = "Saudi Arabia",
                          "RS" = "Serbia",
                          "SG" = "Singapore",
                          "SL" = "Sierra Leone",
                          "SK" = "Slovakia",
                          "ZA" = "South Africa",
                          "KR" = "South Korea",
                          "ES" = "Spain",
                          "CH" = "Switzerland",
                          "TW" = "Taiwan",
                          "TH" = "Thailand",
                          "NL" = "Netherlands",
                          "TT" = "Trinidad & Tobago",
                          "TR" = "Turkey",
                          "UA" = "Ukraine",
                          "AE" = "United Arab Emirates",
                          "UK" = "United Kingdom",
                          "US" = "United States",
                          "UZ" = "Uzbekistan",
                          "VN" = "Vietnam",
                          "ZW" = "Zimbabwe",
                          "ZB" = "Zimbabwe",
                          "OM" = "Oman")) 

# remove NA countries 0.24% of data
d <- d %>%
  filter(!is.na(Country))

# add cultural category label
d <- d %>%
  mutate(culture = case_when(
    Country %in% c("Argentina", "Albania","Australia", "Austria", "Belgium", "Brazil", 
                   "Bulgaria", "Canada", "Chile", "China", "Costa Rica", "Croatia", 
                   "Czech Republic", "France", "Germany", "Greece", "Hong Kong", 
                   "Hungary", "Israel", "Italy", "Japan", "Malaysia", "Netherlands", 
                   "New Zealand", "Norway", "Poland", "Portugal", "Russia", 
                   "Serbia", "Singapore", "Slovakia", "Slovenia", "South Africa", 
                   "Spain", "Sweden", "Switzerland", "Taiwan", "United Kingdom", 
                   "United States") ~ "Individualistic",
    Country %in% c("Bangladesh", "Cameroon", "Colombia", "Ecuador", "Ethiopia", 
                   "Egypt", 
                   "Ghana", "India", "Indonesia", "Iran", "Kenya", 
                   "Kuwait", "Malawi", "Mexico", "Morocco", "Namibia", "Nigeria", 
                   "North Macedonia", 
                   "Pakistan", "Peru", "Philippines", "Saudi Arabia", "Oman",
                   "Senegal", "Sierra Leone", "Sri Lanka", "Turkey", "Vietnam", "Zimbabwe") ~ 
      "Collectivistic",
    TRUE ~ "Unknown"
  ))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
demographic_summary <- d %>%
  summarise(
    `Avearge age (Std.)` = sprintf("%.2f (%.2f)", mean(Age, na.rm = TRUE), sd(Age, na.rm = TRUE)),
    `Age Range` = paste(min(Age, na.rm = TRUE), "to", max(Age, na.rm = TRUE)),
    `N. males` = sprintf("%i", sum(Gender == "Man", na.rm = TRUE)),
    `N. female` = sprintf("%i", sum(Gender == "Woman", na.rm = TRUE)),
    `N. non binary` = sprintf("%i", sum(Gender == "Non-binary", na.rm = TRUE)),
    `N. prefer not to respond` = sprintf("%i", sum(Gender ==  "Prefer not to respond", na.rm = TRUE)),
    `N. prefer to self-describe` = sprintf("%i", sum(Gender == "Prefer to self-describe", na.rm = TRUE))
  ) %>%
  pivot_longer(everything(), names_to = "Demographic", values_to = "Value") 

# knitr::kable(demographic_summary, booktabs = TRUE, 
#              caption = "Demographic Information of Participants", 
#              col.names = c("Demographic", "Value"))%>%
#   kable_styling(latex_options = c("scale_down","striped"))

knitr::kable(demographic_summary, booktabs = TRUE, 
             caption = "Demographic Information of Participants", 
             col.names = c("Demographic", "Value"))
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
demographic_summary <- d %>%
  filter(!is.na(culture)) %>%
  group_by(culture) %>%
  summarise(
    `N participants` = sprintf("%i", n()),
    `Average age (SD)` = sprintf(
      "%.2f (%.2f)",
      mean(Age, na.rm = TRUE),
      sd(Age, na.rm = TRUE)
    ),
    `Age range` = sprintf(
      "%g to %g",
      min(Age, na.rm = TRUE),
      max(Age, na.rm = TRUE)
    ),
    `N males` = sprintf("%i", sum(Gender == "Man", na.rm = TRUE)),
    `N females` = sprintf("%i", sum(Gender == "Woman", na.rm = TRUE)),
    `N non-binary` = sprintf("%i", sum(Gender == "Non-binary", na.rm = TRUE)),
    `N prefer not to respond` = sprintf(
      "%i",
      sum(Gender == "Prefer not to respond", na.rm = TRUE)
    ),
    `N prefer to self-describe` = sprintf(
      "%i",
      sum(Gender == "Prefer to self-describe", na.rm = TRUE)
    ),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols = -culture,
    names_to = "Demographic",
    values_to = "Value"
  ) %>%
  pivot_wider(
    names_from = culture,
    values_from = Value
  ) %>%
  select(
    Demographic,
    Individualistic,
    Collectivistic
  )

# knitr::kable(
#   demographic_summary,
#   booktabs = TRUE,
#   caption = "Demographic Information of Participants by Cultural Classification",
#   col.names = c(
#     "Demographic",
#     "Individualistic",
#     "Collectivistic"
#   )
# ) %>%
#   kable_styling(
#     latex_options = c("scale_down", "striped")
#   )

knitr::kable(
  demographic_summary,
  booktabs = TRUE,
  caption = "Demographic Information of Participants by Cultural Classification",
  col.names = c(
    "Demographic",
    "Individualistic",
    "Collectivistic")) 
```

\newpage

```{r}
#| echo: FALSE

library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)

education_table <- d %>%
  filter(!is.na(Edu), !is.na(culture)) %>%
  mutate(
    Edu = factor(
      Edu,
      levels = c(
        "Less than a high school or secondary school degree (or equivalent)",
        "High school or secondary school degree (or equivalent)",
        "Bachelor’s degree (or equivalent)",
        "Postgraduate degree (MA, PhD, JD, etc.)",
        "Prefer not to respond"
      )
    )
  ) %>%
  count(culture, Edu, name = "N") %>%
  complete(culture, Edu, fill = list(N = 0)) %>%
  group_by(culture) %>%
  mutate(
    percent = 100 * N / sum(N),
    `N (%)` = sprintf("%s (%.1f%%)", format(N, big.mark = ","), percent)
  ) %>%
  ungroup() %>%
  select(Education = Edu, culture, `N (%)`) %>%
  pivot_wider(
    names_from = culture,
    values_from = `N (%)`
  )

# education_table %>%
#   kable(
#     # format = "latex",
#     booktabs = TRUE,
#     escape = TRUE,
#     align = c("l", "c", "c"),
#     col.names = c(
#       "Education level",
#       "Collectivistic, N (\\%)",
#       "Individualistic, N (\\%)"
#     ),
#     caption = "Level of education by cultural group."
#   ) %>%
#   kable_styling(
#     latex_options = c("hold_position", "striped"),
#     full_width = FALSE,
#     position = "center"
#   ) %>%
#   column_spec(1, width = "8cm") %>%
#   column_spec(2:3, width = "3cm")

education_table %>%
  knitr::kable(
    align = c("l", "c", "c"),
    col.names = c(
      "Education level",
      "Collectivistic, N (%)",
      "Individualistic, N (%)"
    ),
    caption = "Level of education by cultural group."
  )
```

\newpage

### Use of external resources


```{r, echo=FALSE}
d %>%
  mutate(
    participant = row_number(),
    condition = case_when(
      feedback == "F"  & justification == "NJ" ~ "Feedback",
      feedback == "NF" & justification == "J"  ~ "Justification",
      feedback == "F"  & justification == "J"  ~ "Feedback + justification",
      .default = "Baseline"
    ),
    condition = factor(
      condition,
      levels = c(
        "Baseline",
        "Feedback",
        "Justification",
        "Feedback + justification"
      )
    )
  ) %>%
  select(
    participant,
    condition,
    matches("^ext_resources_use_[1-6]$")
  ) %>%
  pivot_longer(
    cols = matches("^ext_resources_use_[1-6]$"),
    names_to = "problem",
    names_pattern = "ext_resources_use_(\\d+)",
    values_to = "ext_resources",
    values_drop_na = TRUE
  ) %>%
  mutate(
    problem = factor(
      paste("Problem", problem),
      levels = paste("Problem", 1:6)
    ),
    ext_resources = case_when(
      ext_resources == "Yes" ~ 1,
      ext_resources == "No"  ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  group_by(problem, condition) %>%
  summarise(
    percent = 100 * mean(ext_resources, na.rm = TRUE),
    N = sum(ext_resources, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    result = sprintf("%.2f%% (N = %d)", percent, N)
  ) %>%
  select(problem, condition, result) %>%
  pivot_wider(
    names_from = condition,
    values_from = result
  ) %>%
  knitr::kable(
    booktabs = TRUE,
    align = c("l", "c", "c", "c", "c"),
    caption = paste(
      "Percentage and number of responses reporting use of external",
      "resources, split by problem and condition."
    )
  ) #%>%
  # kableExtra::kable_styling(
  #   latex_options = c("scale_down", "striped"),
  #   font_size = 9,
  #   full_width = FALSE,
  #   position = "center"
  # )

```

\newpage

### Familiarity


```{r, echo=FALSE}
d %>%
  mutate(
    participant = row_number(),
    condition = case_when(
      feedback == "F"  & justification == "NJ" ~ "Feedback",
      feedback == "NF" & justification == "J"  ~ "Justification",
      feedback == "F"  & justification == "J"  ~ "Feedback + justification",
      .default = "Baseline"
    ),
    condition = factor(
      condition,
      levels = c(
        "Baseline",
        "Feedback",
        "Justification",
        "Feedback + justification"
      )
    )
  ) %>%
  select(
    participant,
    condition,
    starts_with("familiarity")
  ) %>%
  pivot_longer(
    cols = starts_with("familiarity"),
    names_to = "problem",
    names_pattern = ".*_(\\d+)$",
    values_to = "familiarity",
    values_drop_na = TRUE
  ) %>%
  mutate(
    problem = factor(
      paste("Problem", problem),
      levels = paste("Problem", 1:6)
    ),
    familiarity = case_when(
      familiarity == "Yes" ~ 1,
      familiarity == "No"  ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  group_by(problem, condition) %>%
  summarise(
    percent = 100 * mean(familiarity, na.rm = TRUE),
    N = sum(familiarity, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    result = sprintf("%.2f%% (N = %d)", percent, N)
  ) %>%
  select(problem, condition, result) %>%
  pivot_wider(
    names_from = condition,
    values_from = result
  ) %>%
  knitr::kable(
    booktabs = TRUE,
    align = c("l", "c", "c", "c", "c"),
    caption = paste(
      "Percentage and number of participants reporting familiarity,",
      "split by problem and condition."
    )
  ) # %>%
  # kableExtra::kable_styling(
  #   latex_options = c("scale_down", "striped"),
  #   font_size = 9,
  #   full_width = FALSE,
  #   position = "center"
  # )
```

\newpage

### Language background

```{r, echo=FALSE}
library(gt)

# Clean the fluency labels
d_lang <- d %>%
  mutate(
    lang_fluency_clean = case_when(
      str_detect(lang_fluency, "^Beginner") ~ "Beginner",
      str_detect(lang_fluency, "^Intermediate") ~ "Intermediate",
      str_detect(lang_fluency, "^Advanced") ~ "Advanced",
      str_detect(lang_fluency, "^Expert/Proficient") ~ "Expert/Proficient",
      lang_fluency == "Prefer not to respond" ~ "Prefer not to respond",
      TRUE ~ NA_character_
    )
  )

# Overall native-language distribution
native_summary <- d_lang %>%
  filter(!is.na(native_lang)) %>%
  count(response = native_lang) %>%
  mutate(
    section = "Native speaker of the study language",
    denominator = sum(n),
    percent = 100 * n / denominator
  )

# Fluency distribution, conditional on reporting non-native status
fluency_summary <- d_lang %>%
  filter(
    native_lang == "No",
    !is.na(lang_fluency_clean)
  ) %>%
  count(response = lang_fluency_clean) %>%
  mutate(
    section = "Fluency among non-native speakers",
    denominator = sum(n),
    percent = 100 * n / denominator
  )

language_table <- bind_rows(
  native_summary,
  fluency_summary
) %>%
  mutate(
    response = factor(
      response,
      levels = c(
        "Yes", "No", "Prefer not to respond",
        "Beginner", "Intermediate", "Advanced",
        "Expert/Proficient"
      )
    )
  ) %>%
  arrange(section, response) %>%
  select(section, response, n, percent)

language_table %>%
  gt(groupname_col = "section") %>%
  cols_label(
    response = "Response",
    n = "N",
    percent = "%"
  ) %>%
  fmt_number(
    columns = percent,
    decimals = 1
  ) %>%
  tab_header(
    title = "Language background of participants"
  ) %>%
  tab_source_note(
    source_note = paste(
      "Fluency was assessed only among participants who reported",
      "that the study language was not their native language."
    )
  )
```

```{r data_preparation_2, include=FALSE}
d <- d %>%
  mutate(participant = row_number())


# --- individual differences measures ---

# belief in evolution [evolution] << this is a single item

# evolution, IH_score, AOT_score, IC_HI, IC_VI, IC_HC, IC_VC, GCBS_score, CRS_score

# ------------------------------------------------------------------------------
# ------------------------------------------------------------------------------
# Intellectual humility; https://www.tandfonline.com/doi/full/10.1080/15298868.2017.1361861

#  self-reported intellectual humility, [IH_1 - IH_9]
# Items in the scale
IH_items <- paste0("IH_", 1:9)

# Negatively worded items
IH_reverse <- c("IH_6", "IH_8", "IH_9")

# Response coding
likert_1_7 <- c(
  "Strongly disagree"          = 1,
  "Moderately disagree"        = 2,
  "Slightly disagree"          = 3,
  "Neither agree nor disagree" = 4,
  "Slightly agree"             = 5,
  "Moderately agree"           = 6,
  "Strongly agree"             = 7
)

d <- d %>%
  # Convert text responses to numbers
  mutate(across(all_of(IH_items),
                ~ unname(likert_1_7[as.character(.x)]))) %>%
  
  # Reverse-score negatively worded items
  mutate(across(all_of(IH_reverse),
                ~ 8 - .x)) %>%
  
  # Overall scale score
  mutate(IH_score = rowMeans(across(all_of(IH_items)), na.rm = FALSE))

# Cronbach's alpha
IH_alpha <- psych::alpha(
  d[, IH_items],
  check.keys = FALSE
)

# IH_alpha

# ------------------------------------------------------------------------------
# ------------------------------------------------------------------------------
# open-mindedness, and [AOT_1 - AOT_13]; https://www.mdpi.com/2079-3200/11/2/27

# Items in the scale
AOT_items <- paste0("AOT_", 1:13)

# reverse scoring
AOT_reverse <- c("AOT_2", "AOT_4", "AOT_5", "AOT_6", "AOT_7", "AOT_8", "AOT_10", "AOT_13")

# Response coding
likert_1_6 <- c(
  "Strongly disagree"          = 1,
  "Moderately disagree"        = 2,
  "Slightly disagree"          = 3,
  "Slightly agree"             = 4,
  "Moderately agree"           = 5,
  "Strongly agree"             = 6
)

d <- d %>%
  # Convert text responses to numbers
  mutate(across(all_of(AOT_items),
                ~ unname(likert_1_6[as.character(.x)]))) %>%
  
  # Reverse-score negatively worded items
  mutate(across(all_of(AOT_reverse),
                ~ 7 - .x)) %>%
  
  # Overall scale score
  mutate(AOT_score = rowMeans(across(all_of(AOT_items)), na.rm = FALSE))

# Cronbach's alpha
AOT_alpha <- psych::alpha(
  d[, AOT_items],
  check.keys = FALSE
)

# AOT_alpha

# ------------------------------------------------------------------------------
# ------------------------------------------------------------------------------
# individualistic and collectivistic cultural tendencies [IC_1 - IC_16]
# https://doi.org/10.1037/0022-3514.74.1.118

# there are 4 factors in this scale (vertical vs horizontal and individualistic vs collectivistic)

HI_items <- paste0("IC_", 1:4)
VI_items <- paste0("IC_", 5:8)
HC_items <- paste0("IC_", 9:12)
VC_items <- paste0("IC_", 13:16)

IC_items <- paste0("IC_", 1:16)

d <- d %>%
  
  # Convert responses to numeric 1-9
  mutate(across(all_of(IC_items),
                ~ as.numeric(sub(" .*", "", as.character(.x))))) %>%
  
  # Compute the four subscale scores
  mutate(
    IC_HI = rowSums(across(all_of(HI_items)), na.rm = FALSE),
    IC_VI = rowSums(across(all_of(VI_items)), na.rm = FALSE),
    IC_HC = rowSums(across(all_of(HC_items)), na.rm = FALSE),
    IC_VC = rowSums(across(all_of(VC_items)), na.rm = FALSE)
  )

# reliability per subscale?
IC_HI_alpha <- psych::alpha(d[, HI_items], check.keys = FALSE)
IC_VI_alpha <- psych::alpha(d[, VI_items], check.keys = FALSE)
IC_HC_alpha <- psych::alpha(d[, HC_items], check.keys = FALSE)
IC_VC_alpha <- psych::alpha(d[, VC_items], check.keys = FALSE)


# ------------------------------------------------------------------------------
# ------------------------------------------------------------------------------
# cospiracy beliefs
# https://doi.org/10.1016/j.jrp.2022.104315
# Generic conspiracists beliefs [GCBS_1_terror GCBS_2_alien GCBS_3_tech GCBS_4_events GCBS_5_exp]

# Items
GCBS_items <- c(
  "GCBS_1_terror",
  "GCBS_2_alien",
  "GCBS_3_tech",
  "GCBS_4_events",
  "GCBS_5_exp"
)

# Response coding
GCBS_codes <- c(
  "Strongly disagree"    = 1,
  "Moderately disagree"  = 2,
  "Slightly disagree"    = 3,
  "Slightly agree"       = 4,
  "Moderately agree"     = 5,
  "Strongly agree"       = 6
)

d <- d %>%
  # Convert responses to numeric
  mutate(across(all_of(GCBS_items),
                ~ unname(GCBS_codes[as.character(.x)]))) %>%
  
  # Total conspiracy-belief score
  mutate(
    GCBS_score = rowSums(across(all_of(GCBS_items)), na.rm = FALSE)
  )

# 
GCBS_alpha <- psych::alpha(d[, GCBS_items], check.keys = FALSE)


# ------------------------------------------------------------------------------
# ------------------------------------------------------------------------------
# centrality of religiosity scale [CRS_1 - CRS_7]
# https://www.mdpi.com/2077-1444/3/3/710

CRS_items <- paste0("CRS", 1:7)

d <- d %>%
  mutate(
    # Item 1: belief in God/divine
    CRS1 = case_when(
      CRS1 == "Not at all"      ~ 1,
      CRS1 == "Not very much"   ~ 2,
      CRS1 == "Moderately"      ~ 3,
      CRS1 == "Quite a bit"     ~ 4,
      CRS1 == "Very much so"    ~ 5,
      TRUE ~ NA_real_
    ),

    # Items 2-3: prayer / meditation
    across(
      c(CRS2, CRS3),
      ~ case_when(
        .x %in% c("Several times a day", "Once a day") ~ 5,
        .x == "More than once a week"                  ~ 4,
        .x %in% c("Once a week", "One to three times a month") ~ 3,
        .x %in% c("A few times a year", "Less often")  ~ 2,
        .x == "Never"                                  ~ 1,
        TRUE ~ NA_real_
      )
    ),

    # Item 4: religious services
    CRS4 = case_when(
      CRS4 %in% c("More than once a week", "Once a week") ~ 5,
      CRS4 == "One to three times a month"                ~ 4,
      CRS4 == "A few times a year"                        ~ 3,
      CRS4 == "Less often"                                ~ 2,
      CRS4 == "Never"                                     ~ 1,
      TRUE ~ NA_real_
    ),

    # Items 5-7: frequency questions
    across(
      c(CRS5, CRS6, CRS7),
      ~ case_when(
        .x == "Never"       ~ 1,
        .x == "Rarely"      ~ 2,
        .x == "Occasionally"~ 3,
        .x == "Often"       ~ 4,
        .x == "Very often"  ~ 5,
        TRUE ~ NA_real_
      )
    ),

    # CRSi-7 score
    CRS_score = rowMeans(across(all_of(CRS_items)), na.rm = FALSE)
  )

CRS_alpha <- psych::alpha(d[, CRS_items], check.keys = FALSE)

# ------------------------------------------------------------------------------
# ------------------------------------------------------------------------------
# last: recode evolution question numerically

d <- d %>%
  mutate(
    evolution_code = case_when(
      evolution == "God or something divine created human beings pretty much in their present form at one time within the last 10,000 years or so." ~ 1,
      
      evolution == "Human beings have developed over millions of years from less advanced forms of life, but God or something divine guided this process." ~ 2,
      
      evolution == "Human beings have developed over millions of years from less advanced forms of life, and God or something divine had no part in this process." ~ 3,
      
      TRUE ~ NA_real_
    )
  )

#  evolution_code
# 1 = Creation
# 2 = Guided evolution
# 3 = Evolution without divine guidance

# ------------------------------------------------------------------------------
# ------------------------------------------------------------------------------
# wrangling into long format

d_crt_long <- d %>%
  # ID + cols matching 'crt#_i' or 'crt#_r'
  select(participant, Country, culture, justification, feedback, matches('^crt[1-6]_[ir]$'), evolution_code, IH_score, AOT_score, IC_HI, IC_VI, IC_HC, IC_VC, GCBS_score, CRS_score, LabID, Sample, calib_int, calib_ref) %>% 
  pivot_longer(
    cols = matches('^crt[1-6]_[ir]$'),
    names_to = 'item',
    values_to = 'response'
  ) %>%
  extract( # Extract 'problem' number and 'condition' from 'item'
    item, 
    into = c('crt', 'problem', 'condition'),
    regex = '(crt)([1-6])_([ir])'
  ) %>%
  mutate(
    problem = as.integer(problem),
    condition = recode(condition, 'i' = 'intuitive', 'r' = 'reflective')
  ) %>%
  select(participant, problem, condition, response, justification, feedback, Country, culture, evolution_code, IH_score, AOT_score, IC_HI, IC_VI, IC_HC, IC_VC, GCBS_score, CRS_score, LabID, Sample, calib_int, calib_ref)

# Pivot familiarity data (one value per participant-problem)
d_fam_long <- d %>%
  pivot_longer(
    cols = matches("^familiarity_[1-6]$"),
    names_to = "fam_item",
    values_to = "familiarity"
  ) %>%
  mutate(problem = as.integer(str_extract(fam_item, "[1-6]"))) %>%
  select(participant, problem, familiarity)

# Pivot ext_resources_use data (one value per participant-problem)
d_ext_long <- d %>%
  pivot_longer(
    cols = matches("^ext_resources_use_[1-6]$"),
    names_to = "ext_item",
    values_to = "ext_resources_use"
  ) %>%
  mutate(problem = as.integer(str_extract(ext_item, "[1-6]"))) %>%
  select(participant, problem, ext_resources_use)

# Pivot dot_crt responses (one value per participant-problem)
d_dot_long <- d %>%
  pivot_longer(
    cols = matches("^dot_crt[1-6]$"),
    names_to = "dot_item",
    values_to = "dot_response"
  ) %>%
  mutate(problem = as.integer(str_extract(dot_item, "[1-6]"))) %>%
  select(participant, problem, dot_response)

# correct answers to dot problems (double checked on Qualtrics) *** MATTEO: TO CHECK; OK 
dot_correct <- c(3,2,4,2,1, 3)
d_dot_long <- d_dot_long %>%
  mutate(dot_accuracy = ifelse(dot_response==dot_correct[d_dot_long$problem], 1, 0))

# Join everything together
d_long <- d_crt_long %>%
  left_join(d_fam_long, by = c("participant","problem")) %>%
  left_join(d_ext_long, by = c("participant","problem")) %>%
  left_join(d_dot_long, by = c("participant","problem")) %>%
  # Now each (participant, problem) has two rows (for each phase),
  # and familiarity and ext_resources_use are duplicated for both.
  select(participant, response, justification, feedback, problem, 
         condition, problem, familiarity, ext_resources_use, dot_accuracy, 
         Country, culture, evolution_code, IH_score, AOT_score, IC_HI, IC_VI, IC_HC, IC_VC, GCBS_score, CRS_score, LabID, Sample, calib_int, calib_ref)



# compute accuracy
d_long$accuracy <- ifelse(!is.na(d_long$response), 
                       ifelse(d_long$response==1,1,0),
                       d_long$response)

# prepare for modelling
d_all <- d_long %>%
  pivot_wider(
    names_from = condition,
    values_from = c(response, accuracy),
    names_sep = "_")

write_csv(d_all, "JT003-EC-data-OK-long.csv")


# for hypothesis H1 we had a slightly different exclusion criteria (familiarity) applied here:
d_all_H1 <- d_all %>%
  filter(ext_resources_use=="No", 
         familiarity=="No",
         dot_accuracy==1)

# next compute dependent variables for specific hypotheses:
dat_H1 <- d_all_H1 %>%
  filter(accuracy_intuitive == 1 | accuracy_reflective == 1) %>% # keep only correct, either at phase 1 or 2
  filter(!is.na(accuracy_intuitive)) %>% # excluded missing responses in phase 1
  mutate(correct_phase2 = ifelse(accuracy_intuitive == 0, accuracy_reflective, 0)) %>%
  select(correct_phase2, participant, problem, justification, feedback, Country, culture, evolution_code, IH_score, AOT_score, IC_HI, IC_VI, IC_HC, IC_VC, GCBS_score, CRS_score, LabID, Sample, calib_int, calib_ref)

# and for the other hypotheses 
dat_Hother <- d_all %>%
  filter(accuracy_intuitive == 0,        # keep only intuitive errors
         ext_resources_use=="No") %>%    # exclude also external resource use
  mutate(corrected = accuracy_reflective) %>%
  select(corrected, participant, problem, justification, feedback, Country, culture, evolution_code, IH_score, AOT_score, IC_HI, IC_VI, IC_HC, IC_VC, GCBS_score, CRS_score, LabID, Sample, calib_int, calib_ref)

# recode conditions as dummy variables for modelling
dat_H1$justification <- ifelse(dat_H1$justification=="J", 1, 0)
dat_H1$feedback <- ifelse(dat_H1$feedback=="F", 1, 0)

dat_Hother$justification <- ifelse(dat_Hother$justification=="J", 1, 0)
dat_Hother$feedback <- ifelse(dat_Hother$feedback=="F", 1, 0)
```

\newpage

## Confirmatory Analyses

```{r, echo=FALSE, warning=FALSE}
mean_accuracy_table <- d_all_H1 %>%
  filter(!is.na(accuracy_intuitive))  %>%
  group_by(justification, feedback, problem) %>%
  summarise(intuitive = mean(accuracy_intuitive),
            reflective = mean(accuracy_reflective))

knitr::kable(mean_accuracy_table,
             booktabs = TRUE, 
             caption = "Mean accuracy by CRT problem and phase (here 'intuitive' is phase 1 and 'reflective' is phase 2). Computed after applying exclusion criteria based on on familiarity and use of external resource.",
             digits=2) # %>%
#  kable_styling(latex_options = c("scale_down","striped"))
```



```{r}
#| fig-align: 'center'
#| echo: FALSE
#| fig-width: 4
#| fig-height: 3
#| fig-cap: "Probability that a correct decision is made in phase 2 rather than in phase 1 (H1 variable), split by country and culture. Error bars are standard errors between participants in each country."
#| label: fig-pH1

dat_H1 %>%
  filter(feedback==0,
         justification==0) %>%
  group_by(Country, culture, participant) %>%
  summarise(correct_phase2 = mean(correct_phase2)) %>%
  group_by(Country, culture) %>%
  summarise(se = mlisi::bootMeanSE(correct_phase2),
            y = mean(correct_phase2)) %>%
  mutate(x_coord = ifelse(culture=="Collectivistic", 
                          rnorm(n(), -0.1, 0.18),
                          rnorm(n(), 1.1, 0.18))) %>%
  ggplot(aes( y=y, group=culture))+
  geom_hline(yintercept = 0.5, lty=2) +
  geom_errorbar(aes(x=x_coord, ymin=y-se, ymax=y+se), width=0, color="dark grey")+
  geom_point(aes(x=x_coord, color=culture))+
  ml_theme() +
  coord_cartesian(ylim=c(0,1), xlim=c(-0.5, 1.5))+
  scale_x_continuous(breaks=c(0,1),
                     labels=c("Collectivistic",
                              "Individualistic"))+
  labs(y="Pr. correct decision made in phase 2",
       x="")+
  scale_color_discrete(guide="none")
    
```

```{r models_H1, include=FALSE}
# fit models for H1
mH1_all <- glmer(correct_phase2 ~ feedback * justification + 
   (feedback * justification||Country), 
   family = binomial("logit"), data = dat_H1, 
   control = glmerControl(optimizer = "bobyqa", 
      optCtrl = list(maxfun = 1e5)))

# fit country_group-level models for individualistic and collectivistic
mH1_i <- glmer(correct_phase2 ~ feedback * justification + 
   (feedback * justification||Country), 
   family = binomial("logit"), 
   data = dat_H1[dat_H1$culture == "Individualistic", ], 
   control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))


mH1_c <- glmer(correct_phase2 ~ feedback * justification + 
   (feedback * justification||Country), 
   family = binomial("logit"), 
   data = dat_H1[dat_H1$culture == "Collectivistic", ], 
   control = glmerControl(optimizer = "bobyqa", 
      optCtrl = list(maxfun = 1e5)))

# ------------------------------------------------------------------------
# test hypotheses

alpha <- 0.05
# note: the tests on separate country_groups are independent one another 
# (different countries, participants, labs, etc.), so the expected 
# false positive rate of the composite test, run on the 2 country_group 
# separately and using the conventional alpha = 0.05 for each test, 
# would be 0.05^2 = 0.0025 (the hypothesis supported if and only if 
# all 2 independent tests are significant). We don't also apply correction 
# for multiple comparisons otherwise it would become too conservative.
 
# -----------
# H1 
 
# One-tailed test for H1a
# Testing if the intercept is significantly less than 0
b_H1a <- fixef(mH1_all)["(Intercept)"]
SE_H1a <- sqrt(diag(vcov(mH1_all))["(Intercept)"])
z_H1a <- b_H1a / SE_H1a
p_value_H1a <- pnorm(z_H1a) # left-tailed test
H1a <- ifelse(p_value_H1a < alpha, 1, 0)
 
# One-tailed tests for H1b 
models <- list(mH1_i, mH1_c)
names <- c("Individualistic", "Collectivistic")
H1b_pvals <- numeric(length(models))
H1b_results <- numeric(length(models))
 
for (i in 1:length(models)) {
  b <- fixef(models[[i]])["(Intercept)"]
  SE <- sqrt(diag(vcov(models[[i]]))["(Intercept)"])
  z <- b / SE
  p_value <- pnorm(z) # left-tailed test
  H1b_pvals[i] <- p_value
  H1b_results[i] <- ifelse(p_value < alpha, 1, 0)
}

names(H1b_pvals) <- names
names(H1b_results) <- names

# complete test
H1b <- ifelse(all(H1b_results == 1), 1, 0)


### CUSTOM FUNCTION TO PRESENT MODEL OUTPUT

model_table <- function(model, caption = NULL, group = "Country",
                        term_labels = NULL, digits = 3) {

  # Fixed effects
  tab_fixed <- broom.mixed::tidy(
    model,
    effects = "fixed",
    conf.int = TRUE
  )

  # Optional prettier labels
  if (!is.null(term_labels)) {
    ii <- match(tab_fixed$term, names(term_labels))
    tab_fixed$term[!is.na(ii)] <- term_labels[ii[!is.na(ii)]]
  }

  tab_fixed <- tab_fixed %>%
    transmute(
      Predictor = term,
      Estimate = sprintf(paste0("%.", digits, "f"), estimate),
      SE = sprintf(paste0("%.", digits, "f"), std.error),
      `95% CI` = sprintf(
        paste0("[%.", digits, "f, %.", digits, "f]"),
        conf.low, conf.high
      ),
      `p-value` = case_when(
        p.value < .001 ~ "< .001",
        TRUE ~ sub("^0", "", sprintf("%.3f", p.value))
      )
    )

  # Random-effect SDs
  vc <- as.data.frame(lme4::VarCorr(model)) %>%
    filter(is.na(var2))  # retain SDs, not correlations

  # Remove suffixes such as Country.1 generated by ||
  vc$grp <- sub("\\.[0-9]+$", "", vc$grp)

  # Apply same labels to random slopes, if supplied
  if (!is.null(term_labels)) {
    ii <- match(vc$var1, names(term_labels))
    vc$var1[!is.na(ii)] <- term_labels[ii[!is.na(ii)]]
  }

  tab_random <- vc %>%
    filter(grp != "Residual") %>%
    transmute(
      Predictor = paste0("SD (", grp, ": ", var1, ")"),
      Estimate = sprintf(paste0("%.", digits, "f"), sdcor),
      SE = "",
      `95% CI` = "",
      `p-value` = ""
    )

  # Model information
  n <- nobs(model)

  n_groups <- if (group %in% names(model.frame(model))) {
    dplyr::n_distinct(model.frame(model)[[group]])
  } else {
    NA_integer_
  }

  tab_info <- tibble(
    Predictor = c("N", paste0("N ", group)),
    Estimate = c(as.character(n), as.character(n_groups)),
    SE = "",
    `95% CI` = "",
    `p-value` = ""
  )

  # Combine and print
  bind_rows(
    tab_fixed,
    tab_random,
    tab_info
  ) %>%
    knitr::kable(
      caption = caption,
      align = c("l", "r", "r", "c", "r")
    )
}

```

\newpage

### Models for H1a and H1b(Correction during deliberation)

```{r, include=FALSE}
# fit overall model
m_all <- glmer(corrected ~ feedback * justification + 
   (feedback * justification||Country), 
   family = binomial("logit"), 
   data = dat_Hother, 
   control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))


# fit country_group-level models for weird and non-weird
m_i <- glmer(corrected ~ feedback * justification + 
   (feedback * justification||Country), 
  family = binomial("logit"), 
  data = dat_Hother[dat_Hother$culture == "Individualistic", ], 
  control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))


m_c <- glmer(corrected ~ feedback * justification + 
   (feedback * justification||Country), 
  family = binomial("logit"), 
  data = dat_Hother[dat_Hother$culture == "Collectivistic", ], 
  control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))

alpha <- 0.05

# -----------
# H2
 
# feedback increases correction rate
 
# One-tailed test for H2a
# Testing if the coefficient for 'feedback' is significantly greater than 0
b_H2a <- fixef(m_all)["feedback"]
SE_H2a <- sqrt(diag(vcov(m_all))["feedback"])
z_H2a <- b_H2a / SE_H2a
p_value_H2a <- 1 - pnorm(z_H2a) # right-tailed test
H2a <- ifelse(p_value_H2a < alpha, 1, 0)
 
# One-tailed tests for H2b
models <- list(m_i, m_c)
names <- c("Individualistic", "Collectivistic")
H2b_pvals <- numeric(length(models))
H2b_results <- numeric(length(models))
 
for (i in 1:length(models)) {
  b <- fixef(models[[i]])["feedback"]
  SE <- sqrt(diag(vcov(models[[i]]))["feedback"])
  z <- b / SE
  p_value <- 1 - pnorm(z) # right-tailed test
  H2b_pvals[i] <- p_value
  H2b_results[i] <- ifelse(p_value < alpha, 1, 0)
}

names(H2b_pvals) <- names
names(H2b_results) <- names

# -----------
# H3
 
# justification increases correction rate
 
# One-tailed test for H3a
# Testing if the coefficient for 'justification' is significantly greater than 0
b_H3a <- fixef(m_all)["justification"]
SE_H3a <- sqrt(diag(vcov(m_all))["justification"])
z_H3a <- b_H3a / SE_H3a
p_value_H3a <- 1 - pnorm(z_H3a) # right-tailed test
H3a <- ifelse(p_value_H3a < alpha, 1, 0)
 
# One-tailed tests for H3b 
models <- list(m_i, m_c)
names <- c("Individualistic", "Collectivistic")
H3b_pvals <- numeric(length(models))
H3b_results <- numeric(length(models))
 
for (i in 1:length(models)) {
  b <- fixef(models[[i]])["justification"]
  SE <- sqrt(diag(vcov(models[[i]]))["justification"])
  z <- b / SE
  p_value <- 1 - pnorm(z) # right-tailed test
  H3b_pvals[i] <- p_value
  H3b_results[i] <- ifelse(p_value < alpha, 1, 0)
}
 
names(H3b_pvals) <- names
names(H3b_results) <- names
```

```{r}

model_table(mH1_all, caption="Model for H2a and H3a.")
```

```{r}
# mH1_i, mH1_c
model_table(mH1_i, caption="Model for H1b; individidualistic countries.")
model_table(mH1_c, caption="Model for H1b; collectivistic countries.")
```

\newpage

### Models for H2 and H3 (Effects of accuracy and justification)


```{r}
model_table(m_all, caption="Model for H2a and H3a.")
```

```{r}
# mH1_i, mH1_c
model_table(m_i, caption="Model for H2b and H3b; individidualistic countries.")
model_table(m_c, caption="Model for H2b and H3b; collectivistic countries.")
```

\newpage

### Confirmatory hypothesis testing summary

```{r, echo=FALSE}
# Format p-values for display
format_p <- function(p, digits = 3) {
  case_when(
    is.na(p)  ~ NA_character_,
    p < 0.001 ~ "< .001",
    TRUE      ~ sub("^0", "", sprintf(paste0("%.", digits, "f"), p))
  )
}

# Format the two culture-specific p-values
format_culture_p <- function(p) {
  paste0(
    names(p),
    " = ",
    format_p(unname(p)),
    collapse = "; "
  )
}

# Support for each sub-hypothesis
H1a_supported <- H1a == 1
H1b_supported <- all(H1b_results == 1)

H2a_supported <- H2a == 1
H2b_supported <- all(H2b_results == 1)

H3a_supported <- H3a == 1
H3b_supported <- all(H3b_results == 1)


hypothesis_results <- tribble(
  ~Hypothesis, ~Prediction, ~Supported, ~`p-value(s)`,

  "H1a",
  "Less than half of correct answers will arise from error correction during deliberation",
  H1a_supported,
  format_p(p_value_H1a),

  "H1b",
  "Baseline performance is below 50% in both cultural groups",
  H1b_supported,
  format_culture_p(H1b_pvals),

  "H2a",
  "Feedback increases correction overall",
  H2a_supported,
  format_p(p_value_H2a),

  "H2b",
  "Feedback increases correction in both cultural groups",
  H2b_supported,
  format_culture_p(H2b_pvals),

  "H3a",
  "Justification increases correction overall",
  H3a_supported,
  format_p(p_value_H3a),

  "H3b",
  "Justification increases correction in both cultural groups",
  H3b_supported,
  format_culture_p(H3b_pvals)
) %>%
  mutate(
    Supported = case_when(
      is.na(Supported) ~ "Not estimable",
      Supported        ~ "Yes",
      TRUE             ~ "No"
    )
  )



hypothesis_results %>%
  kable(
    booktabs = TRUE,
    align = c("l", "l", "c", "l"),
    caption = paste(
      "Summary of preregistered hypothesis tests after including",
      "by-problem random intercepts"
    )
  ) # %>%
  # kable_styling(
  #   latex_options = c("striped", "hold_position"),
  #   font_size = 9,
  #   full_width = FALSE,
  #   position = "center"
  # ) %>%
  # column_spec(
  #   column = 1,
  #   width = "1.3cm"
  # ) %>%
  # column_spec(
  #   column = 2,
  #   width = "7.5cm"
  # ) %>%
  # column_spec(
  #   column = 3,
  #   width = "2.0cm"
  # ) %>%
  # column_spec(
  #   column = 4,
  #   width = "3.5cm"
  # )
```

\newpage

## Robustness Checks

### Random Effects for CRT Problem

```{r models_H1_check1, include=FALSE}
# fit models for H1
mH1_all <- glmer(correct_phase2 ~ feedback * justification + 
   (feedback * justification||Country)+ (1|problem), 
   family = binomial("logit"), data = dat_H1, 
   control = glmerControl(optimizer = "bobyqa", 
      optCtrl = list(maxfun = 1e5)))

# fit country_group-level models for individualistic and collectivistic
mH1_i <- glmer(correct_phase2 ~ feedback * justification + 
   (feedback * justification||Country)+ (1|problem), 
   family = binomial("logit"), 
   data = dat_H1[dat_H1$culture == "Individualistic", ], 
   control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))


mH1_c <- glmer(correct_phase2 ~ feedback * justification + 
   (feedback * justification||Country)+ (1|problem), 
   family = binomial("logit"), 
   data = dat_H1[dat_H1$culture == "Collectivistic", ], 
   control = glmerControl(optimizer = "bobyqa", 
      optCtrl = list(maxfun = 1e5)))

# ------------------------------------------------------------------------
# test hypotheses

alpha <- 0.05
# note: the tests on separate country_groups are independent one another 
# (different countries, participants, labs, etc.), so the expected 
# false positive rate of the composite test, run on the 2 country_group 
# separately and using the conventional alpha = 0.05 for each test, 
# would be 0.05^2 = 0.0025 (the hypothesis supported if and only if 
# all 2 independent tests are significant). We don't also apply correction 
# for multiple comparisons otherwise it would become too conservative.
 
# -----------
# H1 
 
# One-tailed test for H1a
# Testing if the intercept is significantly less than 0
b_H1a <- fixef(mH1_all)["(Intercept)"]
SE_H1a <- sqrt(diag(vcov(mH1_all))["(Intercept)"])
z_H1a <- b_H1a / SE_H1a
p_value_H1a <- pnorm(z_H1a) # left-tailed test
H1a <- ifelse(p_value_H1a < alpha, 1, 0)
 
# One-tailed tests for H1b 
models <- list(mH1_i, mH1_c)
names <- c("Individualistic", "Collectivistic")
H1b_pvals <- numeric(length(models))
H1b_results <- numeric(length(models))
 
for (i in 1:length(models)) {
  b <- fixef(models[[i]])["(Intercept)"]
  SE <- sqrt(diag(vcov(models[[i]]))["(Intercept)"])
  z <- b / SE
  p_value <- pnorm(z) # left-tailed test
  H1b_pvals[i] <- p_value
  H1b_results[i] <- ifelse(p_value < alpha, 1, 0)
}

names(H1b_pvals) <- names
names(H1b_results) <- names

# complete test
H1b <- ifelse(all(H1b_results == 1), 1, 0)


### CUSTOM FUNCTION TO PRESENT MODEL OUTPUT (updated for crossed random effects)

model_table_2 <- function(model, caption = NULL,
                        term_labels = NULL, digits = 3) {

  # Fixed effects
  tab_fixed <- broom.mixed::tidy(
    model,
    effects = "fixed",
    conf.int = TRUE
  )

  # Optional prettier labels
  if (!is.null(term_labels)) {
    ii <- match(tab_fixed$term, names(term_labels))
    tab_fixed$term[!is.na(ii)] <- term_labels[ii[!is.na(ii)]]
  }

  tab_fixed <- tab_fixed %>%
    transmute(
      Predictor = term,
      Estimate = sprintf(paste0("%.", digits, "f"), estimate),
      SE = sprintf(paste0("%.", digits, "f"), std.error),
      `95% CI` = sprintf(
        paste0("[%.", digits, "f, %.", digits, "f]"),
        conf.low, conf.high
      ),
      `p-value` = case_when(
        p.value < .001 ~ "< .001",
        TRUE ~ sub("^0", "", sprintf("%.3f", p.value))
      )
    )

  # Random-effect SDs
  vc <- as.data.frame(lme4::VarCorr(model)) %>%
    filter(is.na(var2))  # variance/SD terms only

  # Clean suffixes produced by ||, e.g. Country.1
  vc$grp <- sub("\\.[0-9]+$", "", vc$grp)

  # Apply labels also to random slopes
  if (!is.null(term_labels)) {
    ii <- match(vc$var1, names(term_labels))
    vc$var1[!is.na(ii)] <- term_labels[ii[!is.na(ii)]]
  }

  tab_random <- vc %>%
    filter(grp != "Residual") %>%
    transmute(
      Predictor = paste0("SD (", grp, ": ", var1, ")"),
      Estimate = sprintf(paste0("%.", digits, "f"), sdcor),
      SE = "",
      `95% CI` = "",
      `p-value` = ""
    )

  # Model information
  n <- nobs(model)

  # Number of levels for every grouping factor
  ng <- lme4::ngrps(model)

  tab_info <- tibble(
    Predictor = c(
      "N",
      paste0("N ", names(ng))
    ),
    Estimate = c(
      as.character(n),
      as.character(ng)
    ),
    SE = "",
    `95% CI` = "",
    `p-value` = ""
  )

  # Combine and print
  bind_rows(
    tab_fixed,
    tab_random,
    tab_info
  ) %>%
    knitr::kable(
      caption = caption,
      align = c("l", "r", "r", "c", "r")
    )
}

```



```{r, include=FALSE}
# fit overall model
m_all <- glmer(corrected ~ feedback * justification + 
   (feedback * justification||Country)+ (1|problem), 
   family = binomial("logit"), 
   data = dat_Hother, 
   control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))


# fit country_group-level models for weird and non-weird
m_i <- glmer(corrected ~ feedback * justification + 
   (feedback * justification||Country)+ (1|problem), 
  family = binomial("logit"), 
  data = dat_Hother[dat_Hother$culture == "Individualistic", ], 
  control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))


m_c <- glmer(corrected ~ feedback * justification + 
   (feedback * justification||Country)+ (1|problem), 
  family = binomial("logit"), 
  data = dat_Hother[dat_Hother$culture == "Collectivistic", ], 
  control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))

alpha <- 0.05

# -----------
# H2
 
# feedback increases correction rate
 
# One-tailed test for H2a
# Testing if the coefficient for 'feedback' is significantly greater than 0
b_H2a <- fixef(m_all)["feedback"]
SE_H2a <- sqrt(diag(vcov(m_all))["feedback"])
z_H2a <- b_H2a / SE_H2a
p_value_H2a <- 1 - pnorm(z_H2a) # right-tailed test
H2a <- ifelse(p_value_H2a < alpha, 1, 0)
 
# One-tailed tests for H2b
models <- list(m_i, m_c)
names <- c("Individualistic", "Collectivistic")
H2b_pvals <- numeric(length(models))
H2b_results <- numeric(length(models))
 
for (i in 1:length(models)) {
  b <- fixef(models[[i]])["feedback"]
  SE <- sqrt(diag(vcov(models[[i]]))["feedback"])
  z <- b / SE
  p_value <- 1 - pnorm(z) # right-tailed test
  H2b_pvals[i] <- p_value
  H2b_results[i] <- ifelse(p_value < alpha, 1, 0)
}

names(H2b_pvals) <- names
names(H2b_results) <- names

# -----------
# H3
 
# justification increases correction rate
 
# One-tailed test for H3a
# Testing if the coefficient for 'justification' is significantly greater than 0
b_H3a <- fixef(m_all)["justification"]
SE_H3a <- sqrt(diag(vcov(m_all))["justification"])
z_H3a <- b_H3a / SE_H3a
p_value_H3a <- 1 - pnorm(z_H3a) # right-tailed test
H3a <- ifelse(p_value_H3a < alpha, 1, 0)
 
# One-tailed tests for H3b 
models <- list(m_i, m_c)
names <- c("Individualistic", "Collectivistic")
H3b_pvals <- numeric(length(models))
H3b_results <- numeric(length(models))
 
for (i in 1:length(models)) {
  b <- fixef(models[[i]])["justification"]
  SE <- sqrt(diag(vcov(models[[i]]))["justification"])
  z <- b / SE
  p_value <- 1 - pnorm(z) # right-tailed test
  H3b_pvals[i] <- p_value
  H3b_results[i] <- ifelse(p_value < alpha, 1, 0)
}
 
names(H3b_pvals) <- names
names(H3b_results) <- names
```

\newpage

```{r}

model_table_2(mH1_all, caption="Model for H2a and H3a (model with random intercepts for CRT problem).")
```

```{r}
# mH1_i, mH1_c
model_table_2(mH1_i, caption="Model for H1b (model with random intercepts for CRT problem); individidualistic countries.")
model_table_2(mH1_c, caption="Model for H1b (model with random intercepts for CRT problem); collectivistic countries.")
```

\newpage

```{r}
model_table_2(m_all, caption="Model for H2a and H3a (model with random intercepts for CRT problem).")
```

```{r}
# mH1_i, mH1_c
model_table_2(m_i, caption="Model for H2b and H3b (model with random intercepts for CRT problem); individidualistic countries.")
model_table_2(m_c, caption="Model for H2b and H3b (model with random intercepts for CRT problem); collectivistic countries.")
```

\newpage

#### Hypothesis testing summary

```{r, echo=FALSE}
# Format p-values for display
format_p <- function(p, digits = 3) {
  case_when(
    is.na(p)  ~ NA_character_,
    p < 0.001 ~ "< .001",
    TRUE      ~ sub("^0", "", sprintf(paste0("%.", digits, "f"), p))
  )
}

# Format the two culture-specific p-values
format_culture_p <- function(p) {
  paste0(
    names(p),
    " = ",
    format_p(unname(p)),
    collapse = "; "
  )
}

# Support for each sub-hypothesis
H1a_supported <- H1a == 1
H1b_supported <- all(H1b_results == 1)

H2a_supported <- H2a == 1
H2b_supported <- all(H2b_results == 1)

H3a_supported <- H3a == 1
H3b_supported <- all(H3b_results == 1)


hypothesis_results <- tribble(
  ~Hypothesis, ~Prediction, ~Supported, ~`p-value(s)`,

  "H1a",
  "Less than half of correct answers will arise from error correction during deliberation",
  H1a_supported,
  format_p(p_value_H1a),

  "H1b",
  "Baseline performance is below 50% in both cultural groups",
  H1b_supported,
  format_culture_p(H1b_pvals),

  "H2a",
  "Feedback increases correction overall",
  H2a_supported,
  format_p(p_value_H2a),

  "H2b",
  "Feedback increases correction in both cultural groups",
  H2b_supported,
  format_culture_p(H2b_pvals),

  "H3a",
  "Justification increases correction overall",
  H3a_supported,
  format_p(p_value_H3a),

  "H3b",
  "Justification increases correction in both cultural groups",
  H3b_supported,
  format_culture_p(H3b_pvals)
) %>%
  mutate(
    Supported = case_when(
      is.na(Supported) ~ "Not estimable",
      Supported        ~ "Yes",
      TRUE             ~ "No"
    )
  )



hypothesis_results %>%
  kable(
    booktabs = TRUE,
    align = c("l", "l", "c", "l"),
    caption = paste(
      "Summary of preregistered hypothesis tests after including",
      "by-problem random intercepts"
    )
  ) # %>%
  # kable_styling(
  #   latex_options = c("striped", "hold_position"),
  #   font_size = 9,
  #   full_width = FALSE,
  #   position = "center"
  # ) %>%
  # column_spec(
  #   column = 1,
  #   width = "1.3cm"
  # ) %>%
  # column_spec(
  #   column = 2,
  #   width = "7.5cm"
  # ) %>%
  # column_spec(
  #   column = 3,
  #   width = "2.0cm"
  # ) %>%
  # column_spec(
  #   column = 4,
  #   width = "3.5cm"
  # )
```


### Random Effects for Participating Site


```{r models_H1_check2, include=FALSE}
# fit models for H1
mH1_all <- glmer(correct_phase2 ~ feedback * justification + 
   (feedback * justification||Country)+ (1|LabID), 
   family = binomial("logit"), data = dat_H1, 
   control = glmerControl(optimizer = "bobyqa", 
      optCtrl = list(maxfun = 1e5)))

# fit country_group-level models for individualistic and collectivistic
mH1_i <- glmer(correct_phase2 ~ feedback * justification + 
   (feedback * justification||Country)+ (1|LabID), 
   family = binomial("logit"), 
   data = dat_H1[dat_H1$culture == "Individualistic", ], 
   control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))


mH1_c <- glmer(correct_phase2 ~ feedback * justification + 
   (feedback * justification||Country)+ (1|LabID), 
   family = binomial("logit"), 
   data = dat_H1[dat_H1$culture == "Collectivistic", ], 
   control = glmerControl(optimizer = "bobyqa", 
      optCtrl = list(maxfun = 1e5)))

# ------------------------------------------------------------------------
# test hypotheses

alpha <- 0.05
# note: the tests on separate country_groups are independent one another 
# (different countries, participants, labs, etc.), so the expected 
# false positive rate of the composite test, run on the 2 country_group 
# separately and using the conventional alpha = 0.05 for each test, 
# would be 0.05^2 = 0.0025 (the hypothesis supported if and only if 
# all 2 independent tests are significant). We don't also apply correction 
# for multiple comparisons otherwise it would become too conservative.
 
# -----------
# H1 
 
# One-tailed test for H1a
# Testing if the intercept is significantly less than 0
b_H1a <- fixef(mH1_all)["(Intercept)"]
SE_H1a <- sqrt(diag(vcov(mH1_all))["(Intercept)"])
z_H1a <- b_H1a / SE_H1a
p_value_H1a <- pnorm(z_H1a) # left-tailed test
H1a <- ifelse(p_value_H1a < alpha, 1, 0)
 
# One-tailed tests for H1b 
models <- list(mH1_i, mH1_c)
names <- c("Individualistic", "Collectivistic")
H1b_pvals <- numeric(length(models))
H1b_results <- numeric(length(models))
 
for (i in 1:length(models)) {
  b <- fixef(models[[i]])["(Intercept)"]
  SE <- sqrt(diag(vcov(models[[i]]))["(Intercept)"])
  z <- b / SE
  p_value <- pnorm(z) # left-tailed test
  H1b_pvals[i] <- p_value
  H1b_results[i] <- ifelse(p_value < alpha, 1, 0)
}

names(H1b_pvals) <- names
names(H1b_results) <- names

# complete test
H1b <- ifelse(all(H1b_results == 1), 1, 0)

```



```{r, include=FALSE}
# fit overall model
m_all <- glmer(corrected ~ feedback * justification + 
   (feedback * justification||Country)+ (1|LabID), 
   family = binomial("logit"), 
   data = dat_Hother, 
   control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))


# fit country_group-level models for weird and non-weird
m_i <- glmer(corrected ~ feedback * justification + 
   (feedback * justification||Country)+ (1|LabID), 
  family = binomial("logit"), 
  data = dat_Hother[dat_Hother$culture == "Individualistic", ], 
  control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))


m_c <- glmer(corrected ~ feedback * justification + 
   (feedback * justification||Country)+ (1|LabID), 
  family = binomial("logit"), 
  data = dat_Hother[dat_Hother$culture == "Collectivistic", ], 
  control = glmerControl(optimizer = "bobyqa", 
     optCtrl = list(maxfun = 1e5)))

alpha <- 0.05

# -----------
# H2
 
# feedback increases correction rate
 
# One-tailed test for H2a
# Testing if the coefficient for 'feedback' is significantly greater than 0
b_H2a <- fixef(m_all)["feedback"]
SE_H2a <- sqrt(diag(vcov(m_all))["feedback"])
z_H2a <- b_H2a / SE_H2a
p_value_H2a <- 1 - pnorm(z_H2a) # right-tailed test
H2a <- ifelse(p_value_H2a < alpha, 1, 0)
 
# One-tailed tests for H2b
models <- list(m_i, m_c)
names <- c("Individualistic", "Collectivistic")
H2b_pvals <- numeric(length(models))
H2b_results <- numeric(length(models))
 
for (i in 1:length(models)) {
  b <- fixef(models[[i]])["feedback"]
  SE <- sqrt(diag(vcov(models[[i]]))["feedback"])
  z <- b / SE
  p_value <- 1 - pnorm(z) # right-tailed test
  H2b_pvals[i] <- p_value
  H2b_results[i] <- ifelse(p_value < alpha, 1, 0)
}

names(H2b_pvals) <- names
names(H2b_results) <- names

# -----------
# H3
 
# justification increases correction rate
 
# One-tailed test for H3a
# Testing if the coefficient for 'justification' is significantly greater than 0
b_H3a <- fixef(m_all)["justification"]
SE_H3a <- sqrt(diag(vcov(m_all))["justification"])
z_H3a <- b_H3a / SE_H3a
p_value_H3a <- 1 - pnorm(z_H3a) # right-tailed test
H3a <- ifelse(p_value_H3a < alpha, 1, 0)
 
# One-tailed tests for H3b 
models <- list(m_i, m_c)
names <- c("Individualistic", "Collectivistic")
H3b_pvals <- numeric(length(models))
H3b_results <- numeric(length(models))
 
for (i in 1:length(models)) {
  b <- fixef(models[[i]])["justification"]
  SE <- sqrt(diag(vcov(models[[i]]))["justification"])
  z <- b / SE
  p_value <- 1 - pnorm(z) # right-tailed test
  H3b_pvals[i] <- p_value
  H3b_results[i] <- ifelse(p_value < alpha, 1, 0)
}
 
names(H3b_pvals) <- names
names(H3b_results) <- names
```

\newpage

```{r}

model_table_2(mH1_all, caption="Model for H2a and H3a (model with random intercepts for participating site).")
```

```{r}
# mH1_i, mH1_c
model_table_2(mH1_i, caption="Model for H1b (model with random intercepts for participating site); individidualistic countries.")
model_table_2(mH1_c, caption="Model for H1b (model with random intercepts for participating site); collectivistic countries.")
```

\newpage

```{r}
model_table_2(m_all, caption="Model for H2a and H3a (model with random intercepts for participating site).")
```

```{r}
# mH1_i, mH1_c
model_table_2(m_i, caption="Model for H2b and H3b (model with random intercepts for participating site); individidualistic countries.")
model_table_2(m_c, caption="Model for H2b and H3b (model with random intercepts for participating site); collectivistic countries.")
```

\newpage

#### Hypothesis testing summary

```{r, echo=FALSE}
# Format p-values for display
format_p <- function(p, digits = 3) {
  case_when(
    is.na(p)  ~ NA_character_,
    p < 0.001 ~ "< .001",
    TRUE      ~ sub("^0", "", sprintf(paste0("%.", digits, "f"), p))
  )
}

# Format the two culture-specific p-values
format_culture_p <- function(p) {
  paste0(
    names(p),
    " = ",
    format_p(unname(p)),
    collapse = "; "
  )
}

# Support for each sub-hypothesis
H1a_supported <- H1a == 1
H1b_supported <- all(H1b_results == 1)

H2a_supported <- H2a == 1
H2b_supported <- all(H2b_results == 1)

H3a_supported <- H3a == 1
H3b_supported <- all(H3b_results == 1)


hypothesis_results <- tribble(
  ~Hypothesis, ~Prediction, ~Supported, ~`p-value(s)`,

  "H1a",
  "Less than half of correct answers will arise from error correction during deliberation",
  H1a_supported,
  format_p(p_value_H1a),

  "H1b",
  "Baseline performance is below 50% in both cultural groups",
  H1b_supported,
  format_culture_p(H1b_pvals),

  "H2a",
  "Feedback increases correction overall",
  H2a_supported,
  format_p(p_value_H2a),

  "H2b",
  "Feedback increases correction in both cultural groups",
  H2b_supported,
  format_culture_p(H2b_pvals),

  "H3a",
  "Justification increases correction overall",
  H3a_supported,
  format_p(p_value_H3a),

  "H3b",
  "Justification increases correction in both cultural groups",
  H3b_supported,
  format_culture_p(H3b_pvals)
) %>%
  mutate(
    Supported = case_when(
      is.na(Supported) ~ "Not estimable",
      Supported        ~ "Yes",
      TRUE             ~ "No"
    )
  )



hypothesis_results %>%
  kable(
    booktabs = TRUE,
    align = c("l", "l", "c", "l"),
    caption = paste(
      "Summary of preregistered hypothesis tests after including",
      "by-problem random intercepts"
    )
  ) # %>%
  # kable_styling(
  #   latex_options = c("striped", "hold_position"),
  #   font_size = 9,
  #   full_width = FALSE,
  #   position = "center"
  # ) %>%
  # column_spec(
  #   column = 1,
  #   width = "1.3cm"
  # ) %>%
  # column_spec(
  #   column = 2,
  #   width = "7.5cm"
  # ) %>%
  # column_spec(
  #   column = 3,
  #   width = "2.0cm"
  # ) %>%
  # column_spec(
  #   column = 4,
  #   width = "3.5cm"
  # )
```



\newpage

## Exploratory Analyses

### Individual Differences and Corrective Behaviour

```{r}
ind_diff_vars <- c(
  "IH_score",
  "AOT_score",
  "IC_HI",
  "IC_VI",
  "IC_HC",
  "IC_VC"
)

cor_mat <- cor(
  d[, ind_diff_vars],
  use = "pairwise.complete.obs",
  method = "pearson"
)

knitr::kable(
  round(cor_mat, 2),
  caption = "Correlations between individual-difference measures"
)
```


```{r}
# standardize individual difference measures
dat_H1 <- dat_H1 %>%
  mutate(IH_score = scale(IH_score),
         AOT_score = scale(AOT_score),
         IC_HI = scale(IC_HI),
         IC_VI = scale(IC_VI),
         IC_HC = scale(IC_HC),
         IC_VC = scale(IC_VC))

dat_Hother <- dat_Hother %>%
  mutate(IH_score = scale(IH_score),
         AOT_score = scale(AOT_score),
         IC_HI = scale(IC_HI),
         IC_VI = scale(IC_VI),
         IC_HC = scale(IC_HC),
         IC_VC = scale(IC_VC))

# mH1_exploi <- glmer(correct_phase2 ~ (feedback * justification)*(IH_score + AOT_score + IC_HI + IC_VI + IC_HC + IC_VC) +
#    (feedback * justification||Country)+ (1|problem),
#    family = binomial("logit"), data = dat_H1,
#    control = glmerControl(optimizer = "bobyqa",
#       optCtrl = list(maxfun = 1e5)))
# 
# m_all_exploi <- glmer(corrected ~ (feedback * justification)*(IH_score + AOT_score + IC_HI + IC_VI + IC_HC + IC_VC) +
#    (feedback * justification||Country)+ (1|problem),
#    family = binomial("logit"),
#    data = dat_Hother,
#    control = glmerControl(optimizer = "bobyqa",
#      optCtrl = list(maxfun = 1e5)))
# 
# saveRDS(mH1_exploi, "mH1_exploi.RDS")
# saveRDS(m_all_exploi, "m_all_exploi.RDS")

mH1_exploi <- readRDS("mH1_exploi.RDS")
m_all_exploi <- readRDS("m_all_exploi.RDS")
```


```{r}
model_table_2(mH1_exploi, caption="Model for H1, including all individual differences measures as predictors.")
```

\newpage


```{r}
model_table_2(m_all_exploi, caption="Model for H2-H3, including all individual differences measures as predictors.")
```


### Community and Student Sample Differences

```{r, echo=TRUE}
# to check
table(d$Sample)
sum(is.na(d$Sample))

# unique(d$Country[is.na(d$Sample)])
# unique(d$LabID[is.na(d$Sample)])

d %>%
  filter(is.na(Sample)) %>%
  group_by(Country, LabID) %>%
  summarise(N = n())
```


```{r}
mH1_explo_sampletype <- glmer(correct_phase2 ~ (feedback * justification)*Sample +
   (feedback * justification||Country)+ (1|problem),
   family = binomial("logit"), data = dat_H1, #[is.element(dat_H1$Sample, c("Student", "Community")),],
   subset = Sample %in% c("Student", "Community"),
   control = glmerControl(optimizer = "bobyqa",
      optCtrl = list(maxfun = 1e5)))

m_all_explo_sampletype <- glmer(corrected ~ (feedback * justification)*Sample +
   (feedback * justification||Country)+ (1|problem),
   family = binomial("logit"),
   data = dat_Hother, # [is.element(dat_Hother$Sample, c("Student", "Community")),],
   subset = Sample %in% c("Student", "Community"),
   control = glmerControl(optimizer = "bobyqa",
     optCtrl = list(maxfun = 1e5)))
```


```{r}
model_table_2(mH1_explo_sampletype, caption="Model for H1, including sample type (Community vs. Student) as fixed-effect.")

model_table_2(m_all_explo_sampletype, caption="Model for H2-H3, including sample type (Community vs. Student) as fixed-effect.")
```


### Confidence Calibration and Intellectual Humility

```{r}
#| fig-align: 'center'
#| echo: FALSE
#| fig-width: 8
#| fig-height: 4
#| fig-cap: "Number of correct answer (vertical coordinates) plotted as a function of the answer to the calibration responses (e.g. the participant's estimates of their own accuracy; horizontal coordinates). Some jitter added for visibility. Both plots demonstrates substantial over-confidence, since in both cases most points lie below the identity line. For this plot we only excluded problems where participants declared using external resources."
#| label: fig-calibration

tab_correct <- d_all %>%
  filter(# familiarity=="No",
         # dot_accuracy==1,
         ext_resources_use=="No") %>%
  group_by(participant) %>%
  summarise(accuracy_intuitive = sum(accuracy_intuitive, na.rm=T),
            accuracy_reflective = sum(accuracy_reflective, na.rm=T))

tab_calib <- d %>%
  mutate(participant = row_number()) %>%
  select(calib_int, calib_ref, participant, Country, culture) %>%
  merge(., tab_correct, by="participant")

p1 <- tab_calib %>%
  ggplot(aes(y=calib_int, x=accuracy_intuitive)) +
  geom_abline(intercept=0, slope=1, lty=2)+
  geom_jitter(width=0.35, height=0.35, pch=".", col="blue")+
  coord_equal(xlim=c(-0.3,6.3), ylim=c(-0.3,6.3))+
  ggtitle("Intuitive phase")+
  labs(y="participant's estimate",
       x="actual accuracy")+
  ml_theme()

p2 <- tab_calib %>%
  ggplot(aes(y=calib_ref, x=accuracy_reflective)) +
  geom_abline(intercept=0, slope=1, lty=2)+
  geom_jitter(width=0.35, height=0.35, pch=".", col="blue")+
  coord_equal(xlim=c(-0.3,6.3), ylim=c(-0.3,6.3))+
  ggtitle("Reflective phase")+
  labs(y="participant's estimate",
       x="actual accuracy")+
  ml_theme()

p1 + p2
```

```{r, echo=FALSE, message=FALSE}
# library for gamm models
library(mgcv)
```



```{r}
# GAMM analysis: confidence bias modulated by IH?

# ------------------------------------------------------------
# 1. Create participant-level dataset
# ------------------------------------------------------------

tab_calib <- d_all %>%
  filter(ext_resources_use == "No") %>%
  group_by(participant) %>%
  summarise(
    Country = first(Country),
    culture = first(culture),

    IH_score = first(IH_score),

    calib_int = first(calib_int),
    calib_ref = first(calib_ref),

    accuracy_intuitive =
      sum(accuracy_intuitive, na.rm = TRUE),

    accuracy_reflective =
      sum(accuracy_reflective, na.rm = TRUE),

    .groups = "drop"
  ) %>%
  mutate(
    IH_z = as.numeric(scale(IH_score))
  )


# ------------------------------------------------------------
# 2. Fit GAMs separately for the two phases
# ------------------------------------------------------------

m_calib_int <- gam(
  calib_int ~
    s(accuracy_intuitive, k = 7, bs = "cr") +
    s(IH_z, k = 5) +
    ti(
      accuracy_intuitive,
      IH_z,
      k = c(7, 5),
      bs = c("cr", "tp")
    ),
  data = tab_calib,
  method = "REML"
)


m_calib_ref <- gam(
  calib_ref ~
    s(accuracy_reflective, k = 7, bs = "cr") +
    s(IH_z, k = 5) +
    ti(
      accuracy_reflective,
      IH_z,
      k = c(7, 5),
      bs = c("cr", "tp")
    ),
  data = tab_calib,
  method = "REML"
)


# # Model summaries
# summary(m_calib_int)
# summary(m_calib_ref)

# # Diagnostics
# gam.check(m_calib_int)
# gam.check(m_calib_ref)

# ------------------------------------------------------------
# 3. Prediction function
# ------------------------------------------------------------

make_predictions <- function(model, accuracy_var, phase) {

  newdat <- expand_grid(
    accuracy = seq(0, 6, length.out = 121),
    IH_z = c(-1, 0, 1)
  )

  # Rename 'accuracy' to whichever predictor the model uses
  names(newdat)[names(newdat) == "accuracy"] <- accuracy_var

  pr <- predict(
    model,
    newdata = newdat,
    type = "response",
    se.fit = TRUE
  )

  newdat %>%
    mutate(
      fit = as.numeric(pr$fit),
      se = as.numeric(pr$se.fit),
      lower = fit - 1.96 * se,
      upper = fit + 1.96 * se,

      IH = factor(
        IH_z,
        levels = c(-1, 0, 1),
        labels = c(
          "IH: -1 SD",
          "IH: mean",
          "IH: +1 SD"
        )
      ),

      Phase = phase,

      accuracy = .data[[accuracy_var]]
    ) %>%
    select(
      accuracy, IH_z, IH,
      fit, lower, upper, Phase
    )
}


pred_int <- make_predictions(
  m_calib_int,
  "accuracy_intuitive",
  "Intuitive phase"
)

pred_ref <- make_predictions(
  m_calib_ref,
  "accuracy_reflective",
  "Reflective phase"
)

pred_calib <- bind_rows(
  pred_int,
  pred_ref
)

```

```{r, echo=FALSE}
format_p <- function(p, digits = 3) {
  case_when(
    is.na(p)  ~ "",
    p < 0.001 ~ "< .001",
    TRUE      ~ sub("^0", "", sprintf(paste0("%.", digits, "f"), p))
  )
}


gam_model_table <- function(models,
                            caption = NULL,
                            model_labels = NULL,
                            term_labels = NULL,
                            digits = 3) {

  # Allow either a single model or a list of models
  if (inherits(models, "gam")) {
    models <- list(Model = models)
  }

  # Supply model names if none exist
  if (is.null(names(models)) || any(names(models) == "")) {
    names(models) <- paste0("Model ", seq_along(models))
  }

  # Optional prettier model labels
  if (!is.null(model_labels)) {
    ii <- match(names(models), names(model_labels))
    names(models)[!is.na(ii)] <- model_labels[ii[!is.na(ii)]]
  }

  tab <- imap_dfr(models, function(model, model_name) {

    # Parametric terms
    param <- broom::tidy(
      model,
      parametric = TRUE
    ) %>%
      transmute(
        Model = model_name,
        Component = "Parametric",
        Term = term,
        Estimate = sprintf(paste0("%.", digits, "f"), estimate),
        SE = sprintf(paste0("%.", digits, "f"), std.error),
        edf = "",
        `Ref. df` = "",
        Statistic = sprintf(paste0("%.", digits, "f"), statistic),
        p = format_p(p.value, digits)
      )

    # Smooth terms
    smooth <- broom::tidy(
      model,
      parametric = FALSE
    ) %>%
      transmute(
        Model = model_name,
        Component = "Smooth",
        Term = term,
        Estimate = "",
        SE = "",
        edf = sprintf(paste0("%.", digits, "f"), edf),
        `Ref. df` = sprintf(paste0("%.", digits, "f"), ref.df),
        Statistic = sprintf(paste0("%.", digits, "f"), statistic),
        p = format_p(p.value, digits)
      )

    bind_rows(param, smooth)
  })

  # Optional prettier term names
  if (!is.null(term_labels)) {
    ii <- match(tab$Term, names(term_labels))
    tab$Term[!is.na(ii)] <- term_labels[ii[!is.na(ii)]]
  }

  knitr::kable(
    tab,
    format = "pipe",
    align = c("l", "l", "l", "r", "r", "r", "r", "r", "r"),
    caption = caption
  )
}
```


```{r}
gam_model_table(
  list(
    Intuitive = m_calib_int,
    Reflective = m_calib_ref
  ),
  caption = "Generalised additive models predicting participants' estimates of performance.",
  term_labels = c(
    "(Intercept)" = "Intercept",
    "s(accuracy_intuitive)" = "Actual accuracy",
    "s(accuracy_reflective)" = "Actual accuracy",
    "s(IH_z)" = "Intellectual humility",
    "ti(accuracy_intuitive,IH_z)" =
      "Actual accuracy × intellectual humility",
    "ti(accuracy_reflective,IH_z)" =
      "Actual accuracy × intellectual humility"
  )
)
```



```{r}
#| fig-align: 'center'
#| echo: FALSE
#| fig-width: 8
#| fig-height: 4
#| fig-cap: "Intellectual humility and calibration of estimated performance. Generalised additive models (GAMs) predicting participants’ estimated number of correct answers from their actual accuracy and intellectual humility, fitted separately for the intuitive (left) and reflective (right) phases. Lines show model-predicted estimates for intellectual humility at the mean and ±1 SD; shaded bands indicate 95% confidence intervals. The dashed diagonal indicates perfect calibration, such that values above the line reflect overestimation and values below the line reflect underestimation. Intellectual humility was associated with a small overall shift in estimates in the intuitive phase, whereas in the reflective phase it showed a small but significant interaction with actual accuracy."
#| label: fig-calibration-model

ggplot(
  pred_calib,
  aes(
    x = accuracy,
    y = fit,
    colour = IH,
    fill = IH
  )
) +
  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper
    ),
    alpha = 0.15,
    colour = NA
  ) +
  geom_line(linewidth = 1) +

  # Perfect calibration
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = 2
  ) +

  facet_wrap(
    ~Phase,
    nrow = 1
  ) +

  coord_equal(
    xlim = c(0, 6),
    ylim = c(0, 6)
  ) +

  scale_x_continuous(
    breaks = 0:6
  ) +
  scale_y_continuous(
    breaks = 0:6
  ) +

  labs(
    x = "Actual accuracy",
    y = "Predicted estimate of accuracy",
    colour = "Intellectual humility",
    fill = "Intellectual humility"
  ) +

  ml_theme()
```

